Reanalysis Step 4: Propensity Score Analysis with Twang

### 2025-08-31 reanalysis-4-propensity_scores.qmd
logging

# Function to process a single imputation
process_imputation <- function(i, imp_datasets, formula, trees, cache_path, use_caching) {
  # Recreate variables inside function to avoid scoping issues
  library(twang)

@@

    return(list(
      imputation = i,
      result = cached_result,
      trees_used = cached_result$n_trees_used,
      weight_min = round(min(weights), 3),
      weight_max = round(max(weights), 3),
      cached = TRUE,
      time_mins = 0
    ))
  } else {
    imp_start <- Sys.time()

@@

    return(list(
      imputation = i,
      result = result,
      trees_used = result$n_trees_used,
      weight_min = round(min(weights), 3),
      weight_max = round(max(weights), 3),
      cached = FALSE,
      time_mins = imp_time
    ))
  }
}

# Run parallel processing
log_message(paste0("Starting parallel processing of ", n_imputations, " imputations using ", n_cores, " cores"))
parallel_start <- Sys.time()

# Use mclapply on Unix/Mac, parLapply on Windows
if (.Platform$OS.type == "unix") {
  # Unix/Mac - use mclapply
  parallel_results <- mclapply(
    1:n_imputations,
    function(i) process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache),
    mc.cores = n_cores
  )
} else {
  # Windows - use parLapply
  cl <- makeCluster(n_cores)

  # Export necessary objects to cluster
  clusterExport(cl, c(
    "process_imputation", "imputed_datasets", "ps_formula", 
    "n_trees", "cache_dir", "use_cache"
  ), envir = environment())

@@

  # Create wrapper function for parLapply
  parallel_results <- parLapply(cl, 1:n_imputations, function(i) {
    process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache)
  })

@@

# Extract results and build progress dataframe
twang_results <- list()
progress_df <- data.frame(
  Imputation = integer(),
  Trees_Used = integer(),
  Weight_Min = numeric(),
  Weight_Max = numeric(),
  Cached = logical(),
  Time_Minutes = numeric()
)

@@

  progress_df <- rbind(progress_df, data.frame(
    Imputation = res$imputation,
    Trees_Used = res$trees_used,
    Weight_Min = res$weight_min,
    Weight_Max = res$weight_max,
    Cached = res$cached,
    Time_Minutes = res$time_mins
  ))

  # Log individual result
  if (res$cached) {
    log_message(paste0("Imputation ", res$imputation, ": Loaded from cache"))
  } else {
    log_message(paste0("Imputation ", res$imputation, ": Fitted in ", res$time_mins, " minutes"))
  }
}

@@

# Display progress summary with caching and timing information
kable(progress_df, 
      caption = paste0("Twang Model Fitting Progress (Total time: ", parallel_time, " minutes using ", n_cores, " cores)"),
      col.names = c("Imputation", "Trees Used", "Min Weight", "Max Weight", "From Cache", "Time (min)"))
```

>>>>

# Function to process a single imputation
process_imputation <- function(i, imp_datasets, formula, trees, cache_path, use_caching, node_id, log_file_path) {
  # Recreate variables inside function to avoid scoping issues
  library(twang)

  # Log node start
  start_msg <- paste0("Node ", node_id, " started: Processing imputation ", i)
  cat(paste0(Sys.time(), " - ", start_msg, "\n"), file = log_file_path, append = TRUE)

@@

    # Log cache hit
    cache_msg <- paste0("Node ", node_id, " completed: Imputation ", i, " loaded from cache")
    cat(paste0(Sys.time(), " - ", cache_msg, "\n"), file = log_file_path, append = TRUE)

    return(list(
      imputation = i,
      node_id = node_id,
      result = cached_result,
      trees_used = cached_result$n_trees_used,
      weight_min = round(min(weights), 3),
      weight_max = round(max(weights), 3),
      cached = TRUE,
      time_mins = 0
    ))
  } else {
    imp_start <- Sys.time()

@@

    # Log completion
    complete_msg <- paste0("Node ", node_id, " completed: Imputation ", i, " fitted in ", imp_time, " minutes")
    cat(paste0(Sys.time(), " - ", complete_msg, "\n"), file = log_file_path, append = TRUE)

    return(list(
      imputation = i,
      node_id = node_id,
      result = result,
      trees_used = result$n_trees_used,
      weight_min = round(min(weights), 3),
      weight_max = round(max(weights), 3),
      cached = FALSE,
      time_mins = imp_time
    ))
  }
}

# Create node tracking
node_counter <- 0
get_next_node_id <- function() {
  node_counter <<- node_counter + 1
  return(node_counter)
}

# Create assignments of imputations to node IDs
imputation_node_assignments <- data.frame(
  imputation = 1:n_imputations,
  node_id = NA
)

# Assign node IDs based on batch processing
batch_size <- ceiling(n_imputations / ceiling(n_imputations / n_cores))
for (i in 1:n_imputations) {
  imputation_node_assignments$node_id[i] <- get_next_node_id()
}

# Run parallel processing
log_message(paste0("Starting parallel processing of ", n_imputations, " imputations using ", n_cores, " cores"))
log_message(paste0("Node assignments: ", paste(imputation_node_assignments$node_id, collapse = ", ")))
parallel_start <- Sys.time()

# Use mclapply on Unix/Mac, parLapply on Windows
if (.Platform$OS.type == "unix") {
  # Unix/Mac - use mclapply
  parallel_results <- mclapply(
    1:n_imputations,
    function(i) {
      node_id <- imputation_node_assignments$node_id[i]
      process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache, node_id, log_file)
    },
    mc.cores = n_cores
  )
} else {
  # Windows - use parLapply
  cl <- makeCluster(n_cores)

  # Export necessary objects to cluster
  clusterExport(cl, c(
    "process_imputation", "imputed_datasets", "ps_formula", 
    "n_trees", "cache_dir", "use_cache", "imputation_node_assignments", "log_file"
  ), envir = environment())

@@

  # Create wrapper function for parLapply
  parallel_results <- parLapply(cl, 1:n_imputations, function(i) {
    node_id <- imputation_node_assignments$node_id[i]
    process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache, node_id, log_file)
  })

@@

# Extract results and build progress dataframe
twang_results <- list()
progress_df <- data.frame(
  Imputation = integer(),
  Node_ID = integer(),
  Trees_Used = integer(),
  Weight_Min = numeric(),
  Weight_Max = numeric(),
  Cached = logical(),
  Time_Minutes = numeric()
)

@@

  progress_df <- rbind(progress_df, data.frame(
    Imputation = res$imputation,
    Node_ID = res$node_id,
    Trees_Used = res$trees_used,
    Weight_Min = res$weight_min,
    Weight_Max = res$weight_max,
    Cached = res$cached,
    Time_Minutes = res$time_mins
  ))

  # Log individual result summary
  if (res$cached) {
    log_message(paste0("Imputation ", res$imputation, " (Node ", res$node_id, "): Loaded from cache"))
  } else {
    log_message(paste0("Imputation ", res$imputation, " (Node ", res$node_id, "): Fitted in ", res$time_mins, " minutes"))
  }
}

@@

# Display progress summary with caching and timing information
kable(progress_df, 
      caption = paste0("Twang Model Fitting Progress (Total time: ", parallel_time, " minutes using ", n_cores, " cores)"),
      col.names = c("Imputation", "Node ID", "Trees Used", "Min Weight", "Max Weight", "From Cache", "Time (min)"))
```
